TBD

### 2021-03-18 outputs/paper/paper.Rmd
Update format

thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
bibliography: references.bib
---

@@

$$+\sum_{e=Northeast}^{West}\hat \beta_5\cdot Region_e+\hat \beta_{6}\cdot I_{WaveID}+\hat \beta_{7}\cdot I_{Meta:OSmobile}+\hat \beta_{8}\cdot I_{Age>65}+\sum_{i=Independent}^{Republican}\hat \beta_9\cdot PID_i
+\hat \beta_{10}\cdot {Ambivalent\ Sexism}+\hat \beta_{11}\cdot$$ $${Polknow}+\sum_{l=video}^{ad}\hat \beta_{12}\cdot Treat_l+\sum_{m=bidenshit}^{lgbtq}\hat \beta_{13}\cdot Script_m+\hat \beta_{14}\cdot I_{exp\_1\_prompt:\ info}$$

>>>>

header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}

thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
bibliography: references.bib

---

@@

$$+\sum_{e=Northeast}^{West}\hat \beta_5\cdot Region_e+\hat \beta_{6}\cdot I_{WaveID}+\hat \beta_{7}\cdot I_{Meta:OSmobile}+\hat \beta_{8}\cdot I_{Age>65}+\sum_{i=Independent}^{Republican}\hat \beta_9\cdot PID_i$$
$$+\hat \beta_{10}\cdot {Ambivalent\ Sexism}+\hat \beta_{11}\cdot {Polknow}+\sum_{l=video}^{ad}\hat \beta_{12}\cdot Treat_l+\sum_{m=bidenshit}^{lgbtq}\hat \beta_{13}\cdot Script_m+\hat \beta_{14}\cdot I_{exp\_1\_prompt:\ info}$$
